|

### 2024-11-17 doc/paper.qmd
visualisation done

```{python}
#| echo: false
#| output: false

import pickle
import pandas as pd

# Load the results from the existing pickle file for table_1
with open('../data/generated/table_1.pickle', 'rb') as f:
    results = pickle.load(f)

# Load the results from the new pickle file for final_table and summary_stats
with open('../output/em_results.pickle', 'rb') as f:
    em_results = pickle.load(f)

def escape_special_characters(df):
    df.columns = [col.replace('_', '\\_').replace('#', '\\#') for col in df.columns]
    return df

# Custom formatter function
def custom_float_format(x):
    return f"{x:.3f}".lstrip('0') if pd.notnull(x) else ""

def prep_latex_table(df, caption=None, label=None, fontsize='\\fontsize{11}{13}\\selectfont', description=None):
    df = escape_special_characters(df.reset_index(drop=True))  # Drop the index column from output tables for better readability
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)

    latex_table = df.to_latex(
        column_format=column_format,
        index=False, 
        float_format=custom_float_format,
        escape=False  # Important to disable escaping so LaTeX commands in column names are respected
    )

    # Construct description to the table
    full_caption = f"{caption}\\\\\n\\textnormal{{{description}}}" if description else caption

    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        fontsize,  # Set font size for the table
        latex_table,
        f"\\caption{{{full_caption}}}" if full_caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

The replicated Figure 3 from original report by @EC_Report_2024 is shown below, followed by the research design choices and assumptions in @sec-research_design_assumptions, documentation of the replication steps in @sec-replication_steps, a detailed results comparison in @sec-results, and concluding remarks in @sec-conclusion.

Table 1 provides descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score, where countries are sorted in descending order based on their aggregate score. The discussion of replication findings is presented in @sec-results.
```{python}
#| label: final_combined_table
#| echo: false
#| output: asis

# Rename the columns to ensure consistency with paper
em_results['final_combined_table'].rename(columns={
    'item6026': 'Country',
    'EM1': 'EM1 (−)',
    'EM2': 'EM2 (−)',
    'EM3': 'EM3 (+)',
    'EM4': 'EM4 (+)',
    'Aggregate_EM_Score': 'Aggregate EM score'
}, inplace=True)

print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - Country scores for earnings management measures (Sorted by aggregate earnings management)',
    label='tab:final_combined_table',
    description = (
    "\\fontsize{10pt}{12pt}\\selectfont " 
    "The variables are computed from 123,469 firm-year observations for fiscal years 1990 to 1999 across 31 countries and 18,040 non-financial firms. Data are obtained from the Worldscope Database (July 2024 version). The definitions and calculations of EM1-EM4, as well as the aggregate score, are thoroughly presented in Section 4. The sign in the column heading indicates whether higher scores for the respective EM measure imply more earnings management (+) or less earnings management (−)."
    )

))
```

@@

```{python}
#| label: table_1 
#| echo: false
#| output: asis

print(prep_latex_table(
    results['table_1'],
    caption='Replicated table - Descriptive statistics: Number of firm-year observations per country',
    label='tab:table_1'
))
```

>>>>

@@

The replicated figure from original report by @EC_Report_2024 is shown below, followed by the research design choices and assumptions in @sec-research_design_assumptions, documentation of the replication steps in @sec-replication_steps, a detailed results comparison in @sec-results, and concluding remarks in @sec-conclusion.

Figure 1 illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021. Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report. The discussion of replication findings is presented in @sec-results.
```{python}
#| label: fig-market-shares
#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
#| fig-align: center
#| echo: false

import pickle
import matplotlib.pyplot as plt

# Load the figure from the pickle file
with open('../output/figure3_market_shares.pickle', 'rb') as f:
    fig = pickle.load(f)

# Display the figure
fig
```

@@
